---
title: "CANSIM Data Test"
date: "Date produced:`r date()`"
output: html_document
runtime: shiny
---

**Part 1**
Load in the required R packages:
```{r, message=FALSE, warning=FALSE}
#install.packages(pkgs=c('cansim','shiny','rmarkdown','ggplot2','DataExplorer'))
library(cansim)
library(shiny)
library(rmarkdown)
library(ggplot2)
library(DataExplorer)
```

**Part 2**
Load "Health characteristics, annual estimates, by household income quintile and highest level of education" CANSIM data:
```{r}
data<-get_cansim("107-0001")
```

**Part 3**
Exploratory data analysis:
``{r}
DataExplorer::create_report(data)
``

```{r}
headers<-colnames(data)
```

**Part 4**
Data year(s)
```{r echo=FALSE}
checkboxGroupInput("datayr", "",
             choices = c("2015", "2016", "2017", "2018")
)

filtered_data<-reactive({
  return(data[data$REF_DATE%in%input$datayr,])
})
```

##Histogram:
Choose a variable:
x-axis
```{r echo=FALSE}
selectInput("xhist", "",
             choices = headers
)
```

See plot:
```{r echo=FALSE}
renderPlot({
  ggplot(filtered_data(),aes_string(x=input$xhist)) +
  geom_histogram()
})
```

##Box Plot:
Choose variables:
x-axis
```{r echo=FALSE}
selectInput("xbox", "",
             choices = headers
            )
```

y-axis
```{r echo=FALSE}
selectInput("ybox", "",
             choices = headers
            )
```

See plot:
```{r echo=FALSE}
renderPlot({
  ggplot(filtered_data(), aes_string(x=input$xbox, y=input$ybox)) +
  geom_boxplot()
})
```

##Violin Plot:
Choose variables:
x-axis
```{r echo=FALSE}
selectInput("xvio", "",
             choices = headers
            )
```

y-axis
```{r echo=FALSE}
selectInput("yvio", "",
             choices = headers
            )
```

See plot:
```{r echo=FALSE}
renderPlot({
  ggplot(filtered_data(), aes_string(x=input$xvio, y=input$yvio)) +
  geom_violin()
})
```

##Bar Graph:
Choose variables:

x-axis
```{r echo=FALSE}
selectInput("xbar", "",
             choices = headers
            )
```

color - split by
```{r echo=FALSE}
selectInput("ybar", "",
             choices = headers
            )
```

plots - split by
```{r echo=FALSE}
selectInput("zbar", "",
             choices = headers
            )
```

See plot:
```{r echo=FALSE}
renderPlot({
  ggplot(filtered_data(), aes_string(x=input$xbar, color=input$ybar)) +
  geom_bar()+
  facet_wrap(~get(input$zbar))
})
```

##Point Plot:
Choose variables:

x-axis
```{r echo=FALSE}
selectInput("xpoint", "",
             choices = headers
            )
```

y-axis
```{r echo=FALSE}
selectInput("ypoint", "",
             choices = headers
            )
```

color - split by
```{r echo=FALSE}
selectInput("zpoint", "",
             choices = headers
            )
```

plots - split by
```{r echo=FALSE}
selectInput("wpoint", "",
             choices = headers
            )
```

See plot:
```{r echo=FALSE}
renderPlot({
  ggplot(filtered_data(), aes_string(x=input$xpoint, y=input$ypoint, color=input$zpoint))+
  geom_point()+
  facet_wrap(~get(input$wpoint))
})
```

update sept 26